Explore consensus cell types

### 2025-01-23 analyses/cell-type-consensus/exploratory-notebooks/02-explore-consensus-results.Rmd
Apply suggestions from code review
Co-authored-by: Joshua Shapiro <josh.shapiro@ccdatalab.org>

# remove cell line projects from file list
cell_line_projects <- c("SCPCP000020", "SCPCP000024")
results_files <- results_files[!names(results_files) %in% cell_line_projects]
project_ids <- names(results_files) #update project ids to remove cell line projects
```

@@

ggplot(unknown_only, aes(x = project_label, y = percent_cells_annotation)) +
  ggforce::geom_sina(size = 0.1) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        plot.margin = margin(10,10,10,10)) +
  labs(
    x = "", 
    y = "Percent of cells annotated as Unknown"
  )

@@

ggplot(num_celltypes_df, aes(x = project_label, y = num_celltypes)) +
  ggforce::geom_sina(size = 0.1) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = rel(0.9))) +
  labs(
    x = "", 
    y = "Number of cell types"
  )
```

@@

```{r}
all_results_df |> 
  dplyr::filter(consensus_annotation != "Unknown") |> 
  dplyr::group_by(consensus_annotation) |> 
  dplyr::summarize(
    total_libraries = length(library_id),
    min_percentage = min(percent_cells_annotation),
    mean_percentage = round(mean(percent_cells_annotation), 2),
    max_percentage = max(percent_cells_annotation)
  ) |> 
  dplyr::arrange(desc(total_libraries))

>>>>

# remove cell line projects from file list
cell_line_projects <- c("SCPCP000020", "SCPCP000024")
project_ids <- setdiff(project_ids, cell_line_projects) # remove cell line projects
results_files <- results_files[project_ids]
```

@@

ggplot(unknown_only, aes(x = project_label, y = percent_cells_annotation)) +
  ggforce::geom_sina(size = 0.1) +
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5),
        plot.margin = margin(10,10,10,10)) +
  labs(
    x = "", 
    y = "Percent of cells annotated as Unknown"
  )

@@

ggplot(num_celltypes_df, aes(x = num_celltypes)) +
  geom_histogram(binwidth = 1, center = 0) +
  facet_wrap(project_label)
```

@@

```{r}
all_results_df |> 
  dplyr::filter(consensus_annotation != "Unknown") |> 
  dplyr::group_by(consensus_annotation) |> 
  dplyr::summarize(
    total_libraries = dplyr::n(),
    min_percentage = min(percent_cells_annotation),
    mean_percentage = round(mean(percent_cells_annotation), 2),
    median_percentage = median(percent_cells_annotation),
    max_percentage = max(percent_cells_annotation)
  ) |> 
  dplyr::arrange(desc(total_libraries))
